\documentclass[aspectratio=169]{beamer}

% Theme selection
\usetheme{metropolis} % A clean, modern, professional theme
\usecolortheme{spruce} % Gives a nice, academic/cybersecurity dark green/grey feel

% Packages
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{xcolor}

% Custom Colors
\definecolor{CyberBlue}{RGB}{59, 130, 246}
\definecolor{CyberDark}{RGB}{15, 23, 42}

% Title Slide Information
\title{Aegis Digital Forensics Toolkit}
\subtitle{An Enterprise-Grade, Dual-Architecture Triage Suite}
\date{\today}
\author{Presented by: [Your Name/Team]}
\institute{Department of Cybersecurity \& Software Engineering}

\begin{document}

% ---------------------------------------------------
\begin{frame}
    \titlepage
\end{frame}

% ---------------------------------------------------
\begin{frame}{Agenda}
    \tableofcontents
\end{frame}

% ---------------------------------------------------
\section{The Challenge in Modern Forensics}

\begin{frame}{The Challenge in Modern Forensics}
    \textbf{Digital investigations face three critical bottlenecks:}
    \vspace{0.5cm}
    \begin{enumerate}
        \item \textbf{Scale \& Noise:} Investigators must manually parse thousands of log lines and hidden metadata tags.
        \item \textbf{Data Mutilation:} Suspects format drives, delete files, and obfuscate payloads to hide tracks.
        \item \textbf{Collaboration Bottlenecks:} Heavy offline processing environments make remote reporting and stakeholder updates difficult.
    \end{enumerate}
    \vspace{0.5cm}
    \textit{We need a solution that balances heavy offline processing with agile, secure reporting.}
\end{frame}

% ---------------------------------------------------
\section{Aegis Architecture: Desktop vs. Web}

\begin{frame}{Dual-Layered Architecture}
    Our toolkit is purposely built across two distinct environments:
    
    \vspace{0.3cm}
    \begin{columns}
        \column{0.45\textwidth}
        \textbf{1. Python Desktop Client (Offline)}
        \begin{itemize}
            \item Built with \texttt{CustomTkinter}.
            \item Deep OS integration for raw byte carving and offline processing.
            \item Ensures evidence never accidentally leaks to the internet.
        \end{itemize}
        
        \column{0.45\textwidth}
        \textbf{2. Flask Web Dashboard (Remote)}
        \begin{itemize}
            \item Accessible via browser for non-technical managers.
            \item Read-only views and triage reports.
            \item Secure RESTful API structure.
        \end{itemize}
    \end{columns}
\end{frame}

% ---------------------------------------------------
\section{Integrity \& Chain of Custody}

\begin{frame}{Integrity \& Chain of Custody}
    \textbf{Principle:} \textit{If evidence is altered without a log, it is inadmissible in court.}
    
    \vspace{0.5cm}
    To guarantee forensic integrity, Aegis implements an \textbf{Activity Tracker Database}:
    \begin{itemize}
        \item Every action (metadata extraction, hashing, carving) triggers an automated \texttt{INSERT} into a secure MySQL environment.
        \item Captures timestamps, target files, success states, and the specific module used.
        \item Creates an immutable audit trail for the investigator.
    \end{itemize}
\end{frame}

% ---------------------------------------------------
\section{Validation Over Trust: Hash \& Threat Intel}

\begin{frame}{Validation Over Trust}
    \textbf{The Cryptographic Validator Module}
    \vspace{0.3cm}
    
    \begin{columns}
        \column{0.5\textwidth}
        \textbf{Mathematical Proof}
        \begin{itemize}
            \item Utilizes the \texttt{hashlib} library to compute MD5, SHA-1, and SHA-256 signatures in safe, 8192-byte chunks.
        \end{itemize}
        
        \column{0.5\textwidth}
        \textbf{Global Threat Intelligence}
        \begin{itemize}
            \item Integrates directly with the \textbf{VirusTotal API}.
            \item Instead of relying on local assumptions, we query global heuristic databases to flag known malware instantly.
        \end{itemize}
    \end{columns}
\end{frame}

% ---------------------------------------------------
\section{Automating the Triage: Syslog Abstractor}

\begin{frame}{Automating the Triage}
    \textbf{The Sentinel Syslog Abstractor}
    \vspace{0.3cm}
    
    Manual log analysis is prone to human error. Aegis automates this:
    \begin{itemize}
        \item \textbf{Regex Pattern Matching:} We utilize the \texttt{re} library to extract timestamps, hostnames, and messages from standard \texttt{auth.log} formats.
        \item \textbf{Data Structuring:} We map this unstructured text into \textbf{Pandas DataFrames}.
        \item \textbf{Anomaly Detection:} The system mathematically flags IPs with multiple failed SSH login attempts, immediately highlighting brute-force vectors.
    \end{itemize}
\end{frame}

% ---------------------------------------------------
\section{Navigating the Messy Reality}

\begin{frame}{Navigating the Messy Reality}
    Digital evidence is rarely pristine. Aegis includes specialized tools for recovering damaged data:
    
    \vspace{0.5cm}
    \textbf{1. Hexadecimal Data Carving}
    \begin{itemize}
        \item Bypasses corrupted file systems entirely.
        \item Scans raw memory dumps and byte-streams to isolate files using explicitly defined "Magic Headers".
    \end{itemize}
    
    \vspace{0.3cm}
    \textbf{2. Payload Decoder Matrix}
    \begin{itemize}
        \item Translates suspicious Base64, Hexadecimal, and Binary strings back into human-readable plain text using \texttt{binascii}.
    \end{itemize}
\end{frame}

% ---------------------------------------------------
\section{Live Demonstration}

\begin{frame}{Live Demonstration}
    \begin{center}
        \Large \textbf{Live Environment Demonstration}
        
        \vspace{0.5cm}
        \normalsize
        1. Metadata Extraction (EXIF)\\
        2. Cryptographic Validation (EICAR Malware String)\\
        3. Automated Log Abstraction\\
        4. Global Executive Dashboard
    \end{center}
\end{frame}

% ---------------------------------------------------
\section{Conclusion}

\begin{frame}{Conclusion}
    \textbf{Summary:}
    Aegis is not just a collection of scripts; it is an engineered, forensically-sound toolkit. 
    
    \vspace{0.5cm}
    By prioritizing \textbf{Chain of Custody}, \textbf{Automation}, and \textbf{Mathematical Validation}, Aegis allows investigators to focus on solving the case rather than fighting their tools.
    
    \vspace{1cm}
    \begin{center}
        \Large \textbf{Questions \& Answers}
    \end{center}
\end{frame}

\end{document}
